### 2018-02-28 contents/reviews/dmri.tex
Updates from ShareLaTeX

In order to characterize the additional diffusion components in voxels with multiple fibres, changes in DWI acquisition strategies is necessary. A natural extension is to acquire additional diffusion directions. This type of acquisition strategies, which enable higher order diffusion modelling algorithms, are generally referred to as high angular resolution diffusion imaging (HARDI). The most wide-spread strategy is to equally distribute gradient directions as vertices of a triangle-tessellated geodesic sphere \cite{Frank2001}. Alternatively, it is also possible to distribute gradient directions in a rectilinear grid, which forms the basis of diffusion spectral imaging (DSI) \cite{Wedeen2005}. Additional acquisition strategies such as distributing gradient directions across multiple concentric spherical shells are also actively explored \cite{Jeurissen2014a}.

>>>>

In order to characterize the additional diffusion components in voxels with multiple fibres, changes in DWI acquisition strategies is necessary. A natural extension is to acquire additional diffusion directions. This type of acquisition strategies, which enable higher order diffusion modelling algorithms, are generally referred to as high angular resolution diffusion imaging (HARDI). The most wide-spread strategy is to equally distribute gradient directions as vertices of a triangle-tessellated geodesic sphere \cite{Frank2001}. Alternatively, it is also possible to distribute gradient directions in a rectilinear grid, which forms the basis of diffusion spectrum imaging (DSI) \cite{Wedeen2005}. Additional acquisition strategies such as distributing gradient directions across multiple concentric spherical shells are also actively explored \cite{Jeurissen2014a}.

### 2018-02-28 contents/reviews/mri.tex
Updates from ShareLaTeX

\paragraph{Repetition Time}
T1 contrast is adjusted by tuning repetition time (TR), which is the length of relaxation interval between excitation pulses. When TR is long (> 1500 ms), $M_z$ recovers totally, and therefore subsequent excitation will again retain maximal signal strength. When the TR is short (< 600 ms), the $M_z$ has not entirely recovered, and the next excitation pulse will not be able to regain signal strength. Different tissues have different intrinsic T1 differences, and will show strong contrast under short TR. Therefore short TR are said to be T1 weighted.

>>>>

\paragraph{Repetition Time}
T1 contrast is adjusted by tuning repetition time (TR), which is the length of relaxation interval between excitation pulses. When TR is long (\textgreater 1500 ms), $M_z$ recovers totally, and therefore subsequent excitation will again retain maximal signal strength. When the TR is short (
\textless 600 ms), the $M_z$ has not entirely recovered, and the next excitation pulse will not be able to regain signal strength. Different tissues have different intrinsic T1 differences, and will show strong contrast under short TR. Therefore short TR are said to be T1 weighted.
